# Midterm Exam

What to submit:
An **R notebook/html document** that contains the script/output for each question.File name convention for submissions: lastname_firstname_midterm.zip. You have 60 minutes (8:30-9:30 am) to complete the exam. There will be a 10% penalty per 10 minutes for late submissions.  

## Question 1 (25 pt.)
The **iris** data set in the **datasets** package contains 150 cases (rows) and 5 variables (columns). 

### Question 1a
Randomly select half of the cases as training dataset and the remaining half as test dataset. 

```{r, message=FALSE, warning=FALSE}
library(datasets)
df <- iris
set.seed(100)
nrow <- nrow(df)
id <- 1:nrow
train.index <- sort(sample(id,nrow/2))
train.index
test.index <- id[-train.index]
test.index

train.df <- df[train.index,]
test.df <- df[test.index,]

if(!(require(DT))) install.packages("DT")
library(DT)
datatable(train.df,caption = "Training dataset",options = list(pageLength = 5))
datatable(test.df,caption = "Test dataset",options = list(pageLength = 5))
```

### Question 1b
Find out the number of each species (*setosa, versicolor, and virginica*) in the training and test datasets, respectively. 

```{r}
table(train.df$Species)
table(test.df$Species)
```

## Question 2 (25 pt.)
Assume that the probabilities of boy and girl births are **0.505** and **0.495**, respectively. 

### Question 2a
What’s the probability of having exactly 50 boys out of 100 births? **(X = 50)**
```{r}
answer_2a <- dbinom(50,size = 100,prob = 0.505)
print(answer_2a)
```
The answer is **`r answer_2a`**

### Question 2b
What’s the probability of having more than 60 boys out of 100 births? **(X > 60)**

```{r}
answer_2b <- pbinom(60,size = 100,prob = 0.505,lower.tail = FALSE)
print(answer_2b)
```

The answer is **`r answer_2b`**

### Question 2c
What’s the probability of having between 40 and 60 boys out of 100 births? **(40 < X ≤ 60)**

```{r}
answer_2c <- diff(pbinom(c(40,60),size = 100,prob = 0.505))
print(answer_2c)
```
The answer is **`r answer_2c`**

### Question 2d
Plot the density function of the number of boy births out of 100. 

```{r}
x <- 0:100
y <- dbinom(x,size = 100,prob = 0.505)
plot(x,y,type = "b",pch=16)
```



## Question 3 (25 pt.)
If cars arrive randomly at a traffic light following posission distribution at the rate of five every ten seconds. 

### Question 3a
What the probability that exactly 30 cars arrive in the next minute (60 seconds)? (X=30)
```{r}
answer_3a <- dpois(30,lambda = 5*6)
print(answer_3a)
```
The answer is **`r answer_3a`**

### Question 3b
What’s the probability that more than 40 cars arrive in the next minute (60 seconds)? (X>40)
```{r}
answer_3b <- ppois(40,lambda = 5*6,lower.tail = FALSE)
print(answer_3b)
```
The answer is **`r answer_3b`**

### Question 3c
What’s the probability that between 20 and 40 cars arrive in the next minute (60 seconds)? 
```{r}
answer_3c <- diff(ppois(c(20,40),lambda = 5*6))
print(answer_3c)
```
The answer is **`r answer_3c`**

### Question 3d
Plot the density function of 0-100 cars arriving in the next minute (60 seconds).

```{r}
x <- 0:100
y <- dpois(x,lambda = 30)
plot(x,y,type = "b",pch=16)
```



## Question 4 (25 pt.)
The number of customers at a bank each day is found to be normally distributed with mean µ = 250 and standard deviation σ=80. 

### Question 4a

What fraction of days will have more than 300 customers? (X>300)
```{r}
answer_4a <- pnorm(300,mean = 250,sd = 80,lower.tail = FALSE)
print(answer_4a)
```
The answer is **`r answer_4a`**

### Question 4b

What number of customers will be exceeded 10% of the time?

```{r}
answer_4b <- qnorm(0.1,mean = 250,sd = 80,lower.tail = FALSE)
print(answer_4b)
```
The answer is **`r answer_4b`**

### Question 4c
What fraction of days will have between 200 and 300 customers? (200 < X≤ 300)
```{r}
answer_4c <- diff(pnorm(c(200,300),mean = 250,sd = 80))
print(answer_4c)
```
The answer is **`r answer_4c`**

### Question 4d
Plot the density function and create the shaded area between 200 and 300 customers.
```{r}
curve(dnorm(x,mean = 250,sd = 80),from = 0,to = 500)
cord.x <- c(200,seq(200,300,by = 1),300)
cord.y <- c(0,dnorm(seq(200,300,by = 1),mean = 250,sd = 80),0)
polygon(cord.x,cord.y,col="red")

```

